\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-06-08 paper/ms.tex
adding error plots to ms

>>>>

\begin{figure}[tp]
\begin{center}
\includegraphics[width=\textwidth]{figures/error/error.pdf}
\caption{\emph{(left)} The maximum numerical error introduced by the algorithm
    described in the text as a function of the number of \celeriteterm\ terms
    $J$ and data points $N$.
    Each line corresponds to a different $J$ and the error increases with $J$
    as shown in the legend.
    Each point in this figure is the average result across 10 systems with
    randomly sampled parameters.
\emph{(right)} The distribution of fractional error on the log determinant of
    $K$ computed using the algorithm described in the text compared to the
    algorithm implemented in \project{NumPy} \citep{Van-Der-Walt:2011} for the
    same systems shown in the left-hand figure.
    This histogram only includes comparisons for $N \le 2048$ because standard
    methods become computationally expensive for larger systems.
    \figurelabel{error}}
\end{center}
\end{figure}
